---
title: "`rhype`: Work With Hypergraphs In R"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hypergraphs are generalisations of graphs. Graphs connect together vertices in a binary manner, that is that (in a simple graph) each edge will connect two vertices. In a hypergraph, there are still vertices like there are in a graph, but edges are replaced with hyperedges that can connect together any number of vertices. This allows us to represent *higher order interactions* that are useful in the analysis of many systems.

`rhype` allows the user to create hypergraph objects in R from different data structures. It then contains many functions for transforming the hypergraph  or calculating properties of hypergraphs that may lead to deeper insights of the data that it represents.

## Installation

`rhype` is available from CRAN using

```{r installation instructions, eval=FALSE}
install.packages("rhype")
```

or the development version is available from GitHub using

```{r github installation instructions, eval=FALSE}
remotes::install_github("hwarden162/rhype")
```

## Development Information

`rhype` is currently undergoing a large rewrite. The main focus of this is to complete unit testing for all functions to cover unoriented hypergraphs with real coefficients. As this happens there will be bug fixes as well as updates to the way in which `rhype` stores hypergraph objects.

Excitingly, on top of this the development version of `rhype` (v0.3.0.9000 currently avaliable on GitHub) now has functions for finding support graphs and connectivity graphs. These can be used together to find shortest hyperpaths between vertices.
